%start %
\documentclass[]{beamer} 
%\usepackage{beamerthemesplit} %主题风格
\usetheme{madrid}

\usepackage{CJKutf8}


\title{My Beamer template}
%author 的高级形式
\author{
   \texorpdfstring{zhang gang
                   \newline
                   \href{mailto:zhanggang0517@139.com}
                 {\footnotesize\ttfamily{zhanggang0517@139.com}}}
                   {}
   \thanks{hello,world}}
%工作单位
\institute{CMCC}

\begin{document}
\begin{CJK*}{UTF8}{} %中文支持
\CJKfamily{gbsn}
%\maketitle

\begin{frame} %貌似和\maketitle 是一样的意义.
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Outline}
  \tableofcontents[pausesections]
\end{frame}

%添加第一部分，后续会每一个部分一个tex文件．暂时先全部放到一起.
\section{Section 1}
\subsection{subsection 1}
\frame{
  \frametitle{slide 1}
  \begin{example} %例子标签的实例（显示的是绿色的)
    \begin{itemize}
      \item 2 is prime (two divisors: 1 and 2).
        \pause
      \item 3 is prime (two divisors: 1 and 3).
        \pause
      \item 4 is not prime (\alert{three} divisors: 1, 2, and 4).
    \end{itemize}
  \end{example}
  \begin{itemize} %slide里的每个条目
    \item 
      \alert{item1}
    \item item2
  \end{itemize}

  \begin{itemize}%演示递归的条目
    \item item1
      \begin{itemize}
        \item{sub item1}
      \end{itemize}
  \end{itemize}
}
%添加新slide的方法２．
\begin{frame}
  \frametitle{There Is No Largest Prime Number}
  \framesubtitle{The proof uses \textit{reductio ad absurdum}.}
  \begin{theorem}
    There is no largest prime number.
  \end{theorem}
  \begin{proof}
    \begin{enumerate}
      \item<1-> Suppose $p$ were the largest prime number.
      \item<2-> Let $q$ be the product of the first $p$ numbers.
      \item<3-> Then $q + 1$ is not divisible by any of them.
      \item<1-> But $q + 1$ is greater than $1$, thus divisible by some prime
  number not in the first $p$ numbers.\qedhere
    \end{enumerate}
  \end{proof}
  \uncover<4->{The proof used \textit{reductio ad absurdum}.}
\end{frame}
\begin{frame}
  \frametitle{What’s Still To Do?}
  \begin{block}{Answered Questions}
    How many primes are there?
  \end{block}
  \begin{block}{Open Questions}
    Is every even number the sum of two primes?
  \end{block}
\end{frame}
%sectoin 2
\section{Section 2}
\frame{
  \frametitle{slide 3}
  \begin{itemize}
    \item item1
      \begin{itemize}
        \item{sub item1,可以添加中文}
      \end{itemize}
  \end{itemize}
}


\end{CJK*}

\end{document}
